---
title: "Network Parameters Comparison - Young Chicago MSM"
author: "Connor Van Meter"
date: "January 7, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Network Parameters by Partnership Type and Calculation Method for Young MSM (Aged 16-29) in Chicago

In this document, three methods for calculating network parameters will be compared:

1. ARTnet-RADAR Netparams Stand-alone Script - Day of Survey
2. ARTnet-RADAR Netparams Stand-alone Script - 3 Month Offset Method
3. ARTnet Workflow Script for Chicago YMSM

The three above mentioned scripts may be found below.
At the end of the document, the network parameter comparison from the script output is performed.


## 1. ARTnet-RADAR Netparams Script 

```{r ARTnet-RADAR_Netparams_Script_DOS, eval=FALSE}

#[Link to location on Github here... likely in ARTnet-RADAR repo]


##
## 02 - Network parameter analysis for ARTnet-RADAR Model
##

## Packages ##
library("tidyverse")
library("ARTnetData")

## Data ##
d <- ARTnet.wide
l <- ARTnet.long

## Inputs ##
city_name <- "Chicago"
coef_name <- paste0("city2", city_name)


# 0. Data Processing ------------------------------------------------------

## Degree calculations ##

l$ONGOING <- as.numeric(l$ONGOING)
l$ongoing2 <- ifelse(is.na(l$ONGOING), 0, l$ONGOING)
l$ONGOING <- NULL

d <- l %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(ptype == 1) %>%
  group_by(AMIS_ID) %>%
  summarise(deg.main = sum(ongoing2)) %>%
  right_join(d, by = "AMIS_ID")

d <- l %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(ptype == 2) %>%
  group_by(AMIS_ID) %>%
  summarise(deg.casl = sum(ongoing2)) %>%
  right_join(d, by = "AMIS_ID")

# If missing degree, then set to 0
d$deg.main <- ifelse(is.na(d$deg.main), 0, d$deg.main)
d$deg.casl <- ifelse(is.na(d$deg.casl), 0, d$deg.casl)

summary(d$deg.main)
summary(d$deg.casl)

# recoding to truncate degree
d$deg.casl <- ifelse(d$deg.casl > 3, 3, d$deg.casl)
d$deg.main <- ifelse(d$deg.main > 2, 2, d$deg.main)

d$deg.tot <- d$deg.main + d$deg.casl

md <- group_by(d, city2) %>%
  summarise(dm = mean(deg.main), dc = mean(deg.casl), dt = mean(deg.tot))
print(md, n = nrow(md))

round(prop.table(table(d$deg.main, d$deg.casl)), 3)

# Concurrency
d$deg.main.conc <- ifelse(d$deg.main > 1, 1, 0)
d$deg.casl.conc <- ifelse(d$deg.casl > 1, 1, 0)

## one-off calcs ##

# Total MC anal sex partner count
d <- l %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(ptype %in% 1:2) %>%
  group_by(AMIS_ID) %>%
  count() %>%
  rename(count.mc.part = n) %>%
  right_join(d, by = "AMIS_ID")
d$count.mc.part <- ifelse(is.na(d$count.mc.part), 0, d$count.mc.part)

d$count.oo.part <- d$ai.part - d$count.mc.part
d$count.oo.part <- pmax(0, d$count.oo.part)

head(data.frame(d$ai.part, d$count.mc.part, d$count.oo.part), 25)
summary(d$count.oo.part)

# Truncated OO part
d$count.oo.part.trunc <- ifelse(d$count.oo.part > 100, 100, d$count.oo.part)
summary(d$count.oo.part.trunc)
table(d$count.oo.part.trunc)


## Race/Ethnicity
table(d$race.cat)
d$race.cat3 <- rep(NA, nrow(d))
d$race.cat3[d$race.cat == "black"] <- 0
d$race.cat3[d$race.cat == "hispanic"] <- 1
d$race.cat3[d$race.cat %in% c("white", "other")] <- 2
table(d$race.cat, d$race.cat3)

table(l$race.cat, useNA = "always")
table(l$p_race.cat, useNA = "always")
table(l$race.cat, l$p_race.cat, useNA = "always")

l$race.cat3 <- rep(NA, nrow(l))
l$race.cat3[l$race.cat == "black"] <- 0
l$race.cat3[l$race.cat == "hispanic"] <- 1
l$race.cat3[l$race.cat %in% c("white", "other")] <- 2
table(l$race.cat3, useNA = "always")

table(l$p_race.cat, useNA = "always")
l$p_race.cat3 <- rep(NA, nrow(l))
l$p_race.cat3[l$p_race.cat == "black"] <- 0
l$p_race.cat3[l$p_race.cat == "hispanic"] <- 1
l$p_race.cat3[l$p_race.cat %in% c("white", "other")] <- 2
table(l$p_race.cat3, useNA = "always")

# redistribute NAs in proportion to non-missing partner races
probs <- prop.table(table(l$race.cat3, l$p_race.cat3), 1)

imp_black <- which(is.na(l$p_race.cat3) & l$race.cat3 == 0)
l$p_race.cat3[imp_black] <- sample(0:2, length(imp_black), TRUE, probs[1, ])

imp_hisp <- which(is.na(l$p_race.cat3) & l$race.cat3 == 1)
l$p_race.cat3[imp_hisp] <- sample(0:2, length(imp_hisp), TRUE, probs[2, ])

imp_white <- which(is.na(l$p_race.cat3) & l$race.cat3 == 2)
l$p_race.cat3[imp_white] <- sample(0:2, length(imp_white), TRUE, probs[3, ])

table(l$race.cat3, l$p_race.cat3, useNA = "always")


## HIV status

l$p_hiv2 <- ifelse(l$p_hiv == 1, 1, 0)
table(l$p_hiv, l$p_hiv2, useNA = "always")

hiv.combo <- rep(NA, nrow(l))
hiv.combo[l$hiv2 == 0 & l$p_hiv == 0] <- 1
hiv.combo[l$hiv2 == 1 & l$p_hiv == 1] <- 2
hiv.combo[l$hiv2 == 1 & l$p_hiv == 0] <- 3
hiv.combo[l$hiv2 == 0 & l$p_hiv == 1] <- 3
hiv.combo[l$hiv2 == 0 & l$p_hiv == 2] <- 4
hiv.combo[l$hiv2 == 1 & l$p_hiv == 2] <- 5
table(hiv.combo, useNA = "always")

l$hiv.concord <- ifelse(hiv.combo %in% 0:1, 1, 0)
l$hiv.concord.pos <- ifelse(hiv.combo == 2, 1, 0)
table(l$hiv.concord)
table(l$hiv.concord.pos)


# Age Filtering
l <- filter(l, age >= 16 & age <= 29)
nrow(l)

d <- filter(d, age >= 16 & age <= 29)
nrow(d)

## Setup output list ##

out <- list()


# 1. Main model -----------------------------------------------------------

out$main <- list()
lmain <- l[l$ptype == 1, ]


## 1A: edges ##

mod <- glm(deg.main ~ city2,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$main$md.main <- as.numeric(pred)


## 1B: nodematch("age.grp", diff = TRUE) ##

age.breaks <- c(0, 18, 24, 29, 100)
lmain$index.age.grp <- cut(lmain$age, age.breaks, labels = FALSE)
lmain$part.age.grp <- cut(as.numeric(lmain$p_age_imp), age.breaks, labels = FALSE)
data.frame(lmain$age, lmain$index.age.grp, lmain$p_age_imp, lmain$part.age.grp)

lmain$same.age.grp <- ifelse(lmain$index.age.grp == lmain$part.age.grp, 1, 0)

mod <- glm(same.age.grp ~ city2 + index.age.grp,
           data = lmain, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name, index.age.grp = 1:3)
pred <- predict(mod, newdata = dat, type = "response")

out$main$nm.age.grp <- as.numeric(pred)




## 1Bb: nodematch("age.grp", diff = FALSE) ##

mod <- glm(same.age.grp ~ city2,
           data = lmain, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$main$nm.age.grp_diffF <- as.numeric(pred)



## 1C: nodefactor("age.grp") ##

d$age.grp <- cut(d$age, age.breaks, labels = FALSE)

mod <- glm(deg.main ~ city2 + age.grp + sqrt(age.grp),
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, age.grp = 1:3)
pred <- predict(mod, newdata = dat, type = "response")

out$main$nf.age.grp <- as.numeric(pred)



## 1D: nodematch("race", diff = TRUE) ##

prop.table(table(lmain$race.cat3, lmain$p_race.cat3), 1)

lmain$same.race <- ifelse(lmain$race.cat3 == lmain$p_race.cat3, 1, 0)
group_by(lmain, race.cat3) %>%
  summarise(mn = mean(same.race))

mod <- glm(same.race ~ city2 + as.factor(race.cat3),
           data = lmain, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name, race.cat3 = 0:2)
pred <- predict(mod, newdata = dat, type = "response")

out$main$nm.race <- as.numeric(pred)


## 1Db: nodematch("race", diff = FALSE) ##

mod <- glm(same.race ~ city2,
           data = lmain, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$main$nm.race_diffF <- as.numeric(pred)


## 1E: nodefactor("race") ##

mod <- glm(deg.main ~ city2 + as.factor(race.cat3),
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, race.cat3 = 0:2)
pred <- predict(mod, newdata = dat, type = "response")

out$main$nf.race <- as.numeric(pred)



## 1F: nodefactor("deg.casl") ##

mod <- glm(deg.main ~ city2 + deg.casl,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, deg.casl = sort(unique(d$deg.casl)))
pred <- predict(mod, newdata = dat, type = "response")

out$main$nf.deg.casl <- as.numeric(pred)

deg.casl.dist <- prop.table(table(d$deg.casl[d$city2 == city_name]))
out$main$deg.casl.dist <- as.numeric(deg.casl.dist)



## 1G: concurrent ##

mod <- glm(deg.main.conc ~ city2,
           data = d, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$main$concurrent <- as.numeric(pred)


## 1H: nodefactor("diag.status") ##

mod <- glm(deg.main ~ city2 + hiv2,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, hiv2 = 0:1)
pred <- predict(mod, newdata = dat, type = "response")

out$main$nf.diag.status <- as.numeric(pred)



## Durations ##

# overall
durs.main <- lmain %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(ongoing2 == 1) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()

# create city weights
durs.main.geo <- lmain %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(ongoing2 == 1) %>%
  filter(city2 == city_name) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()

# city-specific weight based on ratio of medians
wt <- durs.main.geo$median.dur/durs.main$median.dur

# The weekly dissolution rate is function of the mean of the geometric distribution
# which relates to the median as:
durs.main$rates.main.adj <- 1 - (2^(-1/(wt*durs.main$median.dur)))

# Mean duration associated with a geometric distribution that median:
durs.main$mean.dur.adj <- 1/(1 - (2^(-1/(wt*durs.main$median.dur))))
out$main$durs.main.homog <- durs.main

# stratified by age

# first, non-matched by age group
durs.main.nonmatch <- lmain %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(ongoing2 == 1) %>%
  filter(same.age.grp == 0) %>%
  # group_by(index.age.grp) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()
durs.main.nonmatch$index.age.grp <- 0

# then, matched within age-groups
durs.main.matched <- lmain %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(ongoing2 == 1) %>%
  filter(same.age.grp == 1) %>%
  group_by(index.age.grp) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()
durs.main.matched

durs.main.all <- rbind(durs.main.nonmatch, durs.main.matched)

durs.main.all$rates.main.adj <- 1 - (2^(-1/(wt*durs.main.all$median.dur)))
durs.main.all$mean.dur.adj <- 1/(1 - (2^(-1/(wt*durs.main.all$median.dur))))

durs.main.all <- durs.main.all[, c(3, 1, 2, 4, 5)]
out$main$durs.main.byage <- durs.main.all



# 2. Casual model ---------------------------------------------------------

out$casl <- list()
lcasl <- l[l$ptype == 2, ]


## 2A: edges ##

mod <- glm(deg.casl ~ city2,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$md.casl <- as.numeric(pred)


## 2B: nodematch("age.grp", diff = TRUE) ##

lcasl$index.age.grp <- cut(lcasl$age, age.breaks, labels = FALSE)
lcasl$part.age.grp <- cut(as.numeric(lcasl$p_age_imp), age.breaks, labels = FALSE)
data.frame(lcasl$age, lcasl$index.age.grp, lcasl$p_age_imp, lcasl$part.age.grp)

lcasl$same.age.grp <- ifelse(lcasl$index.age.grp == lcasl$part.age.grp, 1, 0)

mod <- glm(same.age.grp ~ city2 + index.age.grp,
           data = lcasl, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name, index.age.grp = 1:3)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nm.age.grp <- as.numeric(pred)

# Consider adding absdiff within index.age.grp
# group_by(lcasl, index.age.grp) %>%
#   summarise(absdiff = mean(abs(age - p_age_imp)))
#
# abs(lcasl$age - lcasl$p_age_imp)


## 2B: nodematch("age.grp", diff = FALSE) ##

mod <- glm(same.age.grp ~ city2,
           data = lcasl, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nm.age.grp_diffF <- as.numeric(pred)


## 2C: nodefactor("age.grp") ##

d$age.grp <- cut(d$age, age.breaks, labels = FALSE)

mod <- glm(deg.casl ~ city2 + age.grp + sqrt(age.grp),
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, age.grp = 1:3)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nf.age.grp <- as.numeric(pred)


## 2D: nodematch("race") ##

prop.table(table(lcasl$race.cat3, lcasl$p_race.cat3), 1)

lcasl$same.race <- ifelse(lcasl$race.cat3 == lcasl$p_race.cat3, 1, 0)

mod <- glm(same.race ~ city2 + as.factor(race.cat3),
           data = lcasl, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name, race.cat3 = 0:2)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nm.race <- as.numeric(pred)


## 2Db: nodematch("race", diff = FALSE) ##

mod <- glm(same.race ~ city2,
           data = lcasl, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nm.race_diffF <- as.numeric(pred)


## 2E: nodefactor("race", diff = TRUE) ##

mod <- glm(deg.casl ~ city2 + as.factor(race.cat3),
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, race.cat3 = 0:2)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nf.race <- as.numeric(pred)


## 2F: nodefactor("deg.main") ##

mod <- glm(deg.casl ~ city2 + deg.main,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, deg.main = 0:2)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nf.deg.main <- as.numeric(pred)

deg.main.dist <- prop.table(table(d$deg.main[d$city2 == city_name]))
out$casl$deg.main.dist <- as.numeric(deg.main.dist)


## 2G: concurrent ##

mod <- glm(deg.casl.conc ~ city2,
           data = d, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$concurrent <- as.numeric(pred)


## 2H: nodefactor("diag.status") ##

mod <- glm(deg.casl ~ city2 + hiv2,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, hiv2 = 0:1)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nf.diag.status <- as.numeric(pred)


## Durations ##

# overall
durs.casl <- lcasl %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(ongoing2 == 1) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()

# create city weights
durs.casl.geo <- lcasl %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(ongoing2 == 1) %>%
  filter(city2 == city_name) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()

# city-specific weight based on ratio of medians
wt <- durs.casl.geo$median.dur/durs.casl$median.dur

# The weekly dissolution rate is function of the mean of the geometric distribution
# which relates to the median as:
durs.casl$rates.casl.adj <- 1 - (2^(-1/(wt*durs.casl$median.dur)))

# Mean duration associated with a geometric distribution that median:
durs.casl$mean.dur.adj <- 1/(1 - (2^(-1/(wt*durs.casl$median.dur))))
out$casl$durs.casl.homog <- durs.casl

# stratified by age

# first, non-matched by age group
durs.casl.nonmatch <- lcasl %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(ongoing2 == 1) %>%
  filter(same.age.grp == 0) %>%
  # group_by(index.age.grp) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()
durs.casl.nonmatch$index.age.grp <- 0

# then, matched within age-groups
durs.casl.matched <- lcasl %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(same.age.grp == 1) %>%
  filter(ongoing2 == 1) %>%
  group_by(index.age.grp) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()
durs.casl.matched

durs.casl.all <- rbind(durs.casl.nonmatch, durs.casl.matched)
durs.casl.all

durs.casl.all$rates.casl.adj <- 1 - (2^(-1/(wt*durs.casl.all$median.dur)))
durs.casl.all$mean.dur.adj <- 1/(1 - (2^(-1/(wt*durs.casl.all$median.dur))))

durs.casl.all <- durs.casl.all[, c(3, 1, 2, 4, 5)]
out$casl$durs.casl.byage <- durs.casl.all


# 3. One-off model --------------------------------------------------------

out$inst <- list()
linst <- l[l$ptype == 3, ]

## 3A: edges ##

head(d$count.oo.part, 25)
summary(d$count.oo.part)

# weekly rate
d$rate.oo.part <- d$count.oo.part/52
summary(d$rate.oo.part)

mod <- glm(count.oo.part ~ city2,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")/52

out$inst$md.inst <- as.numeric(pred)


## 3B: nodematch("age.grp", diff = TRUE) ##

linst$index.age.grp <- cut(linst$age, age.breaks, labels = FALSE)
linst$part.age.grp <- cut(as.numeric(linst$p_age_imp), age.breaks, labels = FALSE)
data.frame(linst$age, linst$index.age.grp, linst$p_age_imp, linst$part.age.grp)

linst$same.age.grp <- ifelse(linst$index.age.grp == linst$part.age.grp, 1, 0)

mod <- glm(same.age.grp ~ city2 + index.age.grp,
           data = linst, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name, index.age.grp = 1:3)
pred <- predict(mod, newdata = dat, type = "response")

out$inst$nm.age.grp <- as.numeric(pred)


## 3Bb: nodematch("age.grp", diff = FALSE) ##

mod <- glm(same.age.grp ~ city2,
           data = linst, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$inst$nm.age.grp_diffF <- as.numeric(pred)


## 3C: nodefactor("age.grp") ##

d$age.grp <- cut(d$age, age.breaks, labels = FALSE)

mod <- glm(count.oo.part ~ city2 + age.grp + sqrt(age.grp),
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, age.grp = 1:3)
pred <- predict(mod, newdata = dat, type = "response")/52

out$inst$nf.age.grp <- as.numeric(pred)


## 3D: nodematch("race", diff = TRUE) ##

prop.table(table(linst$race.cat3, linst$p_race.cat3), 1)

linst$same.race <- ifelse(linst$race.cat3 == linst$p_race.cat3, 1, 0)

mod <- glm(same.race ~ city2 + as.factor(race.cat3),
           data = linst, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name, race.cat3 = 0:2)
pred <- predict(mod, newdata = dat, type = "response")

out$inst$nm.race <- as.numeric(pred)


## 3D: nodematch("race", diff = FALSE) ##

mod <- glm(same.race ~ city2,
           data = linst, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$inst$nm.race_diffF <- as.numeric(pred)


## 3E: nodefactor("race") ##

mod <- glm(count.oo.part ~ city2 + as.factor(race.cat3),
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, race.cat3 = 0:2)
pred <- predict(mod, newdata = dat, type = "response")/52

out$inst$nf.race <- as.numeric(pred)


## 3F: nodefactor("risk.grp") ##

# city-specific wts
wt <- mean(d$rate.oo.part[d$city2 == city_name], na.rm = TRUE)/mean(d$rate.oo.part, na.rm = TRUE)
wt.rate <- d$rate.oo.part * wt

oo.quants <- rep(NA, 5)
sr <- sort(wt.rate)
qsize <- floor(length(sr) / 5)
oo.quants[1] <- mean(sr[1:qsize])
oo.quants[2] <- mean(sr[((1*qsize)+1):(2*qsize)])
oo.quants[3] <- mean(sr[((2*qsize)+1):(3*qsize)])
oo.quants[4] <- mean(sr[((3*qsize)+1):(4*qsize)])
oo.quants[5] <- mean(sr[((4*qsize)+1):length(sr)])

# Weekly acquisition rate
oo.quants

# Yearly OO partner count
oo.quants * 52

# New OO partner every X years
1/(oo.quants * 52)

# New OO partner every weeks
1/oo.quants

# Save it
out$inst$nf.risk.grp <- oo.quants


## 3G: nodefactor("deg.tot") ##

d$deg.tot3 <- ifelse(d$deg.tot >= 3, 3, d$deg.tot)
table(d$deg.tot3)

deg.tot.dist <- prop.table(table(d$deg.tot3[d$city2 == city_name]))
out$inst$deg.tot.dist <- as.numeric(deg.tot.dist)

mod <- glm(count.oo.part ~ city2 + deg.tot3 + sqrt(deg.tot3),
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, deg.tot3 = 0:3)
pred <- predict(mod, newdata = dat, type = "response")/52

out$inst$nf.deg.tot <- as.numeric(pred)


## 3H: nodefactor("diag.status") ##

mod <- glm(count.oo.part ~ city2 + hiv2,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, hiv2 = 0:1)
pred <- predict(mod, newdata = dat, type = "response")/52

out$inst$nf.diag.status <- as.numeric(pred)



# 4. Other Parameters -----------------------------------------------------

## Sexual Role ##

d <- l %>%
  filter(RAI == 1) %>%
  group_by(AMIS_ID) %>%
  count() %>%
  rename(nRAIpart = n) %>%
  right_join(d, by = "AMIS_ID") %>%
  as.data.frame()
d$nRAIpart <- ifelse(is.na(d$nRAIpart), 0, d$nRAIpart)
table(d$nRAIpart, useNA = "always")

d <- l %>%
  filter(IAI == 1) %>%
  group_by(AMIS_ID) %>%
  count() %>%
  rename(nIAIpart = n) %>%
  right_join(d, by = "AMIS_ID") %>%
  as.data.frame()
d$nIAIpart <- ifelse(is.na(d$nIAIpart), 0, d$nIAIpart)
table(d$nIAIpart, useNA = "always")

table(d$nRAIpart, d$nIAIpart, useNA = "always")

# default NA for no AI
roletype <- rep(NA, nrow(d))
roletype[d$nRAIpart == 0 & d$nIAIpart > 0] <- 0
roletype[d$nIAIpart == 0 & d$nRAIpart > 0] <- 1
roletype[d$nIAIpart > 0 & d$nRAIpart > 0] <- 2
table(roletype, useNA = "always")

out$all$role.type <- prop.table(table(roletype))



# SAVE --------------------------------------------------------------------

# fn <- paste("ARTnetWorkflow/data/artnet.NetParam", gsub(" ", "", city_name), "rda", sep = ".")
# saveRDS(out, file = fn)



#####################################################

## OUTPUTS

## Mean Degree

# Overall
md.overall.main.ARTnet_DOS_script <- out$main$md.main
md.overall.casl.ARTnet_DOS_script <- out$casl$md.casl
md.overall.inst.ARTnet_DOS_script <- out$inst$md.inst

# By Age Group
md.age.main.ARTnet_DOS_script <- out$main$nf.age.grp
md.age.casl.ARTnet_DOS_script <- out$casl$nf.age.grp
md.age.inst.ARTnet_DOS_script <- out$inst$nf.age.grp

# By Race
md.race.main.ARTnet_DOS_script <- out$main$nf.race
md.race.casl.ARTnet_DOS_script <- out$casl$nf.race
md.race.inst.ARTnet_DOS_script <- out$inst$nf.race

# By Diagnosed HIV Status
md.HIV_status.main.ARTnet_DOS_script <- out$main$nf.diag.status
md.HIV_status.casl.ARTnet_DOS_script <- out$casl$nf.diag.status
md.HIV_status.inst.ARTnet_DOS_script <- out$inst$nf.diag.status

# By Cross Partnership Degree
md.casl_cross_deg.main.ARTnet_DOS_script <- out$main$nf.deg.casl
md.main_cross_deg.casl.ARTnet_DOS_script <- out$casl$nf.deg.main


## Proportion Concurrent
prop.concurrent.main.ARTnet_DOS_script <- out$main$concurrent
prop.concurrent.casl.ARTnet_DOS_script <- out$casl$concurrent


## Mixing

# By Age - Overall
mixing.age.overall.main.ARTnet_DOS_script <- out$main$nm.age.grp_diffF
mixing.age.overall.casl.ARTnet_DOS_script <- out$casl$nm.age.grp_diffF
mixing.age.overall.inst.ARTnet_DOS_script <- out$inst$nm.age.grp_diffF

# By Age - Within Age Group
mixing.age.within_group.main.ARTnet_DOS_script <- out$main$nm.age.grp
mixing.age.within_group.casl.ARTnet_DOS_script <- out$casl$nm.age.grp
mixing.age.within_group.inst.ARTnet_DOS_script <- out$inst$nm.age.grp

# By Race - Overall
mixing.race.overall.main.ARTnet_DOS_script <- out$main$nm.race_diffF
mixing.race.overall.casl.ARTnet_DOS_script <- out$casl$nm.race_diffF
mixing.race.overall.inst.ARTnet_DOS_script <- out$inst$nm.race_diffF

# By Race - Within Race Group
mixing.race.within_group.main.ARTnet_DOS_script <- out$main$nm.race
mixing.race.within_group.casl.ARTnet_DOS_script <- out$casl$nm.race
mixing.race.within_group.inst.ARTnet_DOS_script <- out$inst$nm.race


## Mean Duration
duration.main.ARTnet_DOS_script <- durs.main.all$mean.dur.adj
duration.casl.ARTnet_DOS_script <- durs.casl.all$mean.dur.adj


## One-Time Partner Rates 

# By Main+Casual Degree
OTP.rates.by.degree.ARTnet_DOS_script <- out$inst$nf.deg.tot

# By Risk Quintile
OTP.rates.by.risk.ARTnet_DOS_script <- out$inst$nf.risk.grp


```

## 2. ARTnet-RADAR Netparams Script - 3 Month Offset Method

```{r ARTnet-RADAR_Netparams_Script_3MO, eval=FALSE}

##
## 02 - Network parameter analysis for ARTnet-RADAR Model - Three Month Offset
##

## Packages ##
library("tidyverse")
library("ARTnetData")

## Data ##
d <- ARTnet.wide
l <- ARTnet.long

## Inputs ##
city_name <- "Chicago"
coef_name <- paste0("city2", city_name)


# 0. Data Processing ------------------------------------------------------

## Degree calculations ##

l$ONGOING <- as.numeric(l$ONGOING)
l$ongoing2 <- ifelse(is.na(l$ONGOING), 0, l$ONGOING)

prior.month.of.evaluation <- 3
ARTnet.long$ongoing.evaluation.date <- ARTnet.long$SUB_DATE -
  round(prior.month.of.evaluation*30.44)
l$ongoing3 <- ifelse(ARTnet.long$start.date <
                                 ARTnet.long$ongoing.evaluation.date &
                                 ARTnet.long$end.date >
                                 ARTnet.long$ongoing.evaluation.date, 1, 0)
l$ONGOING <- NULL

d <- l %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(ptype == 1) %>%
  group_by(AMIS_ID) %>%
  summarise(deg.main = sum(ongoing3)) %>%
  right_join(d, by = "AMIS_ID")

d <- l %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(ptype == 2) %>%
  group_by(AMIS_ID) %>%
  summarise(deg.casl = sum(ongoing3)) %>%
  right_join(d, by = "AMIS_ID")

# If missing degree, then set to 0
d$deg.main <- ifelse(is.na(d$deg.main), 0, d$deg.main)
d$deg.casl <- ifelse(is.na(d$deg.casl), 0, d$deg.casl)

summary(d$deg.main)
summary(d$deg.casl)

# recoding to truncate degree
d$deg.casl <- ifelse(d$deg.casl > 3, 3, d$deg.casl)
d$deg.main <- ifelse(d$deg.main > 2, 2, d$deg.main)

d$deg.tot <- d$deg.main + d$deg.casl

md <- group_by(d, city2) %>%
  summarise(dm = mean(deg.main), dc = mean(deg.casl), dt = mean(deg.tot))
print(md, n = nrow(md))

round(prop.table(table(d$deg.main, d$deg.casl)), 3)

# Concurrency
d$deg.main.conc <- ifelse(d$deg.main > 1, 1, 0)
d$deg.casl.conc <- ifelse(d$deg.casl > 1, 1, 0)

## one-off calcs ##

# Total MC anal sex partner count
d <- l %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(ptype %in% 1:2) %>%
  group_by(AMIS_ID) %>%
  count() %>%
  rename(count.mc.part = n) %>%
  right_join(d, by = "AMIS_ID")
d$count.mc.part <- ifelse(is.na(d$count.mc.part), 0, d$count.mc.part)

d$count.oo.part <- d$ai.part - d$count.mc.part
d$count.oo.part <- pmax(0, d$count.oo.part)

head(data.frame(d$ai.part, d$count.mc.part, d$count.oo.part), 25)
summary(d$count.oo.part)

# Truncated OO part
d$count.oo.part.trunc <- ifelse(d$count.oo.part > 100, 100, d$count.oo.part)
summary(d$count.oo.part.trunc)
table(d$count.oo.part.trunc)


## Race/Ethnicity
table(d$race.cat)
d$race.cat3 <- rep(NA, nrow(d))
d$race.cat3[d$race.cat == "black"] <- 0
d$race.cat3[d$race.cat == "hispanic"] <- 1
d$race.cat3[d$race.cat %in% c("white", "other")] <- 2
table(d$race.cat, d$race.cat3)

table(l$race.cat, useNA = "always")
table(l$p_race.cat, useNA = "always")
table(l$race.cat, l$p_race.cat, useNA = "always")

l$race.cat3 <- rep(NA, nrow(l))
l$race.cat3[l$race.cat == "black"] <- 0
l$race.cat3[l$race.cat == "hispanic"] <- 1
l$race.cat3[l$race.cat %in% c("white", "other")] <- 2
table(l$race.cat3, useNA = "always")

table(l$p_race.cat, useNA = "always")
l$p_race.cat3 <- rep(NA, nrow(l))
l$p_race.cat3[l$p_race.cat == "black"] <- 0
l$p_race.cat3[l$p_race.cat == "hispanic"] <- 1
l$p_race.cat3[l$p_race.cat %in% c("white", "other")] <- 2
table(l$p_race.cat3, useNA = "always")

# redistribute NAs in proportion to non-missing partner races
probs <- prop.table(table(l$race.cat3, l$p_race.cat3), 1)

imp_black <- which(is.na(l$p_race.cat3) & l$race.cat3 == 0)
l$p_race.cat3[imp_black] <- sample(0:2, length(imp_black), TRUE, probs[1, ])

imp_hisp <- which(is.na(l$p_race.cat3) & l$race.cat3 == 1)
l$p_race.cat3[imp_hisp] <- sample(0:2, length(imp_hisp), TRUE, probs[2, ])

imp_white <- which(is.na(l$p_race.cat3) & l$race.cat3 == 2)
l$p_race.cat3[imp_white] <- sample(0:2, length(imp_white), TRUE, probs[3, ])

table(l$race.cat3, l$p_race.cat3, useNA = "always")


## HIV status

l$p_hiv2 <- ifelse(l$p_hiv == 1, 1, 0)
table(l$p_hiv, l$p_hiv2, useNA = "always")

hiv.combo <- rep(NA, nrow(l))
hiv.combo[l$hiv2 == 0 & l$p_hiv == 0] <- 1
hiv.combo[l$hiv2 == 1 & l$p_hiv == 1] <- 2
hiv.combo[l$hiv2 == 1 & l$p_hiv == 0] <- 3
hiv.combo[l$hiv2 == 0 & l$p_hiv == 1] <- 3
hiv.combo[l$hiv2 == 0 & l$p_hiv == 2] <- 4
hiv.combo[l$hiv2 == 1 & l$p_hiv == 2] <- 5
table(hiv.combo, useNA = "always")

l$hiv.concord <- ifelse(hiv.combo %in% 0:1, 1, 0)
l$hiv.concord.pos <- ifelse(hiv.combo == 2, 1, 0)
table(l$hiv.concord)
table(l$hiv.concord.pos)




# Age Filtering
l <- filter(l, age >= 16 & age <= 29)
nrow(l)

d <- filter(d, age >= 16 & age <= 29)
nrow(d)

## Setup output list ##

out <- list()


# 1. Main model -----------------------------------------------------------

out$main <- list()
lmain <- l[l$ptype == 1, ]


## 1A: edges ##

mod <- glm(deg.main ~ city2,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$main$md.main <- as.numeric(pred)


## 1B: nodematch("age.grp", diff = TRUE) ##

age.breaks <- c(0, 18, 24, 29, 100)
lmain$index.age.grp <- cut(lmain$age, age.breaks, labels = FALSE)
lmain$part.age.grp <- cut(as.numeric(lmain$p_age_imp), age.breaks, labels = FALSE)
data.frame(lmain$age, lmain$index.age.grp, lmain$p_age_imp, lmain$part.age.grp)

lmain$same.age.grp <- ifelse(lmain$index.age.grp == lmain$part.age.grp, 1, 0)

mod <- glm(same.age.grp ~ city2 + index.age.grp,
           data = lmain, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name, index.age.grp = 1:3)
pred <- predict(mod, newdata = dat, type = "response")

out$main$nm.age.grp <- as.numeric(pred)




## 1Bb: nodematch("age.grp", diff = FALSE) ##

mod <- glm(same.age.grp ~ city2,
           data = lmain, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$main$nm.age.grp_diffF <- as.numeric(pred)



## 1C: nodefactor("age.grp") ##

d$age.grp <- cut(d$age, age.breaks, labels = FALSE)

mod <- glm(deg.main ~ city2 + age.grp + sqrt(age.grp),
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, age.grp = 1:3)
pred <- predict(mod, newdata = dat, type = "response")

out$main$nf.age.grp <- as.numeric(pred)



## 1D: nodematch("race", diff = TRUE) ##

prop.table(table(lmain$race.cat3, lmain$p_race.cat3), 1)

lmain$same.race <- ifelse(lmain$race.cat3 == lmain$p_race.cat3, 1, 0)
group_by(lmain, race.cat3) %>%
  summarise(mn = mean(same.race))

mod <- glm(same.race ~ city2 + as.factor(race.cat3),
           data = lmain, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name, race.cat3 = 0:2)
pred <- predict(mod, newdata = dat, type = "response")

out$main$nm.race <- as.numeric(pred)


## 1Db: nodematch("race", diff = FALSE) ##

mod <- glm(same.race ~ city2,
           data = lmain, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$main$nm.race_diffF <- as.numeric(pred)


## 1E: nodefactor("race") ##

mod <- glm(deg.main ~ city2 + as.factor(race.cat3),
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, race.cat3 = 0:2)
pred <- predict(mod, newdata = dat, type = "response")

out$main$nf.race <- as.numeric(pred)



## 1F: nodefactor("deg.casl") ##

mod <- glm(deg.main ~ city2 + deg.casl,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, deg.casl = sort(unique(d$deg.casl)))
pred <- predict(mod, newdata = dat, type = "response")

out$main$nf.deg.casl <- as.numeric(pred)

deg.casl.dist <- prop.table(table(d$deg.casl[d$city2 == city_name]))
out$main$deg.casl.dist <- as.numeric(deg.casl.dist)



## 1G: concurrent ##

mod <- glm(deg.main.conc ~ city2,
           data = d, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$main$concurrent <- as.numeric(pred)


## 1H: nodefactor("diag.status") ##

mod <- glm(deg.main ~ city2 + hiv2,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, hiv2 = 0:1)
pred <- predict(mod, newdata = dat, type = "response")

out$main$nf.diag.status <- as.numeric(pred)



## Durations ##

# overall
durs.main <- lmain %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(ongoing3 == 1) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()

# create city weights
durs.main.geo <- lmain %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(ongoing3 == 1) %>%
  filter(city2 == city_name) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()

# city-specific weight based on ratio of medians
wt <- durs.main.geo$median.dur/durs.main$median.dur

# The weekly dissolution rate is function of the mean of the geometric distribution
# which relates to the median as:
durs.main$rates.main.adj <- 1 - (2^(-1/(wt*durs.main$median.dur)))

# Mean duration associated with a geometric distribution that median:
durs.main$mean.dur.adj <- 1/(1 - (2^(-1/(wt*durs.main$median.dur))))
out$main$durs.main.homog <- durs.main

# stratified by age

# first, non-matched by age group
durs.main.nonmatch <- lmain %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(ongoing3 == 1) %>%
  filter(same.age.grp == 0) %>%
  # group_by(index.age.grp) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()
durs.main.nonmatch$index.age.grp <- 0

# then, matched within age-groups
durs.main.matched <- lmain %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(ongoing3 == 1) %>%
  filter(same.age.grp == 1) %>%
  group_by(index.age.grp) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()
durs.main.matched

durs.main.all <- rbind(durs.main.nonmatch, durs.main.matched)

durs.main.all$rates.main.adj <- 1 - (2^(-1/(wt*durs.main.all$median.dur)))
durs.main.all$mean.dur.adj <- 1/(1 - (2^(-1/(wt*durs.main.all$median.dur))))

durs.main.all <- durs.main.all[, c(3, 1, 2, 4, 5)]
out$main$durs.main.byage <- durs.main.all



# 2. Casual model ---------------------------------------------------------

out$casl <- list()
lcasl <- l[l$ptype == 2, ]


## 2A: edges ##

mod <- glm(deg.casl ~ city2,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$md.casl <- as.numeric(pred)


## 2B: nodematch("age.grp", diff = TRUE) ##

lcasl$index.age.grp <- cut(lcasl$age, age.breaks, labels = FALSE)
lcasl$part.age.grp <- cut(as.numeric(lcasl$p_age_imp), age.breaks, labels = FALSE)
data.frame(lcasl$age, lcasl$index.age.grp, lcasl$p_age_imp, lcasl$part.age.grp)

lcasl$same.age.grp <- ifelse(lcasl$index.age.grp == lcasl$part.age.grp, 1, 0)

mod <- glm(same.age.grp ~ city2 + index.age.grp,
           data = lcasl, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name, index.age.grp = 1:3)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nm.age.grp <- as.numeric(pred)

# Consider adding absdiff within index.age.grp
# group_by(lcasl, index.age.grp) %>%
#   summarise(absdiff = mean(abs(age - p_age_imp)))
#
# abs(lcasl$age - lcasl$p_age_imp)


## 2B: nodematch("age.grp", diff = FALSE) ##

mod <- glm(same.age.grp ~ city2,
           data = lcasl, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nm.age.grp_diffF <- as.numeric(pred)


## 2C: nodefactor("age.grp") ##

d$age.grp <- cut(d$age, age.breaks, labels = FALSE)

mod <- glm(deg.casl ~ city2 + age.grp + sqrt(age.grp),
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, age.grp = 1:3)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nf.age.grp <- as.numeric(pred)


## 2D: nodematch("race") ##

prop.table(table(lcasl$race.cat3, lcasl$p_race.cat3), 1)

lcasl$same.race <- ifelse(lcasl$race.cat3 == lcasl$p_race.cat3, 1, 0)

mod <- glm(same.race ~ city2 + as.factor(race.cat3),
           data = lcasl, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name, race.cat3 = 0:2)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nm.race <- as.numeric(pred)


## 2Db: nodematch("race", diff = FALSE) ##

mod <- glm(same.race ~ city2,
           data = lcasl, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nm.race_diffF <- as.numeric(pred)


## 2E: nodefactor("race", diff = TRUE) ##

mod <- glm(deg.casl ~ city2 + as.factor(race.cat3),
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, race.cat3 = 0:2)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nf.race <- as.numeric(pred)


## 2F: nodefactor("deg.main") ##

mod <- glm(deg.casl ~ city2 + deg.main,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, deg.main = 0:2)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nf.deg.main <- as.numeric(pred)

deg.main.dist <- prop.table(table(d$deg.main[d$city2 == city_name]))
out$casl$deg.main.dist <- as.numeric(deg.main.dist)


## 2G: concurrent ##

mod <- glm(deg.casl.conc ~ city2,
           data = d, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$concurrent <- as.numeric(pred)


## 2H: nodefactor("diag.status") ##

mod <- glm(deg.casl ~ city2 + hiv2,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, hiv2 = 0:1)
pred <- predict(mod, newdata = dat, type = "response")

out$casl$nf.diag.status <- as.numeric(pred)


## Durations ##

# overall
durs.casl <- lcasl %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(ongoing3 == 1) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()

# create city weights
durs.casl.geo <- lcasl %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(ongoing3 == 1) %>%
  filter(city2 == city_name) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()

# city-specific weight based on ratio of medians
wt <- durs.casl.geo$median.dur/durs.casl$median.dur

# The weekly dissolution rate is function of the mean of the geometric distribution
# which relates to the median as:
durs.casl$rates.casl.adj <- 1 - (2^(-1/(wt*durs.casl$median.dur)))

# Mean duration associated with a geometric distribution that median:
durs.casl$mean.dur.adj <- 1/(1 - (2^(-1/(wt*durs.casl$median.dur))))
out$casl$durs.casl.homog <- durs.casl

# stratified by age

# first, non-matched by age group
durs.casl.nonmatch <- lcasl %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(ongoing3 == 1) %>%
  filter(same.age.grp == 0) %>%
  # group_by(index.age.grp) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()
durs.casl.nonmatch$index.age.grp <- 0

# then, matched within age-groups
durs.casl.matched <- lcasl %>%
  filter(RAI == 1 | IAI == 1) %>%
  filter(index.age.grp < 4) %>%
  filter(same.age.grp == 1) %>%
  filter(ongoing3 == 1) %>%
  group_by(index.age.grp) %>%
  summarise(mean.dur = mean(duration, na.rm = TRUE),
            median.dur = median(duration, na.rm = TRUE)) %>%
  as.data.frame()
durs.casl.matched

durs.casl.all <- rbind(durs.casl.nonmatch, durs.casl.matched)
durs.casl.all

durs.casl.all$rates.casl.adj <- 1 - (2^(-1/(wt*durs.casl.all$median.dur)))
durs.casl.all$mean.dur.adj <- 1/(1 - (2^(-1/(wt*durs.casl.all$median.dur))))

durs.casl.all <- durs.casl.all[, c(3, 1, 2, 4, 5)]
out$casl$durs.casl.byage <- durs.casl.all


# 3. One-off model --------------------------------------------------------

out$inst <- list()
linst <- l[l$ptype == 3, ]

## 3A: edges ##

head(d$count.oo.part, 25)
summary(d$count.oo.part)

# weekly rate
d$rate.oo.part <- d$count.oo.part/52
summary(d$rate.oo.part)

mod <- glm(count.oo.part ~ city2,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")/52

out$inst$md.inst <- as.numeric(pred)


## 3B: nodematch("age.grp", diff = TRUE) ##

linst$index.age.grp <- cut(linst$age, age.breaks, labels = FALSE)
linst$part.age.grp <- cut(as.numeric(linst$p_age_imp), age.breaks, labels = FALSE)
data.frame(linst$age, linst$index.age.grp, linst$p_age_imp, linst$part.age.grp)

linst$same.age.grp <- ifelse(linst$index.age.grp == linst$part.age.grp, 1, 0)

mod <- glm(same.age.grp ~ city2 + index.age.grp,
           data = linst, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name, index.age.grp = 1:3)
pred <- predict(mod, newdata = dat, type = "response")

out$inst$nm.age.grp <- as.numeric(pred)


## 3Bb: nodematch("age.grp", diff = FALSE) ##

mod <- glm(same.age.grp ~ city2,
           data = linst, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$inst$nm.age.grp_diffF <- as.numeric(pred)


## 3C: nodefactor("age.grp") ##

d$age.grp <- cut(d$age, age.breaks, labels = FALSE)

mod <- glm(count.oo.part ~ city2 + age.grp + sqrt(age.grp),
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, age.grp = 1:3)
pred <- predict(mod, newdata = dat, type = "response")/52

out$inst$nf.age.grp <- as.numeric(pred)


## 3D: nodematch("race", diff = TRUE) ##

prop.table(table(linst$race.cat3, linst$p_race.cat3), 1)

linst$same.race <- ifelse(linst$race.cat3 == linst$p_race.cat3, 1, 0)

mod <- glm(same.race ~ city2 + as.factor(race.cat3),
           data = linst, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name, race.cat3 = 0:2)
pred <- predict(mod, newdata = dat, type = "response")

out$inst$nm.race <- as.numeric(pred)


## 3D: nodematch("race", diff = FALSE) ##

mod <- glm(same.race ~ city2,
           data = linst, family = binomial())
summary(mod)

dat <- data.frame(city2 = city_name)
pred <- predict(mod, newdata = dat, type = "response")

out$inst$nm.race_diffF <- as.numeric(pred)


## 3E: nodefactor("race") ##

mod <- glm(count.oo.part ~ city2 + as.factor(race.cat3),
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, race.cat3 = 0:2)
pred <- predict(mod, newdata = dat, type = "response")/52

out$inst$nf.race <- as.numeric(pred)


## 3F: nodefactor("risk.grp") ##

# city-specific wts
wt <- mean(d$rate.oo.part[d$city2 == city_name], na.rm = TRUE)/mean(d$rate.oo.part, na.rm = TRUE)
wt.rate <- d$rate.oo.part * wt

oo.quants <- rep(NA, 5)
sr <- sort(wt.rate)
qsize <- floor(length(sr) / 5)
oo.quants[1] <- mean(sr[1:qsize])
oo.quants[2] <- mean(sr[((1*qsize)+1):(2*qsize)])
oo.quants[3] <- mean(sr[((2*qsize)+1):(3*qsize)])
oo.quants[4] <- mean(sr[((3*qsize)+1):(4*qsize)])
oo.quants[5] <- mean(sr[((4*qsize)+1):length(sr)])

# Weekly acquisition rate
oo.quants

# Yearly OO partner count
oo.quants * 52

# New OO partner every X years
1/(oo.quants * 52)

# New OO partner every weeks
1/oo.quants

# Save it
out$inst$nf.risk.grp <- oo.quants


## 3G: nodefactor("deg.tot") ##

d$deg.tot3 <- ifelse(d$deg.tot >= 3, 3, d$deg.tot)
table(d$deg.tot3)

deg.tot.dist <- prop.table(table(d$deg.tot3[d$city2 == city_name]))
out$inst$deg.tot.dist <- as.numeric(deg.tot.dist)

mod <- glm(count.oo.part ~ city2 + deg.tot3 + sqrt(deg.tot3),
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, deg.tot3 = 0:3)
pred <- predict(mod, newdata = dat, type = "response")/52

out$inst$nf.deg.tot <- as.numeric(pred)


## 3H: nodefactor("diag.status") ##

mod <- glm(count.oo.part ~ city2 + hiv2,
           data = d, family = poisson())
summary(mod)

dat <- data.frame(city2 = city_name, hiv2 = 0:1)
pred <- predict(mod, newdata = dat, type = "response")/52

out$inst$nf.diag.status <- as.numeric(pred)



# 4. Other Parameters -----------------------------------------------------

## Sexual Role ##

d <- l %>%
  filter(RAI == 1) %>%
  group_by(AMIS_ID) %>%
  count() %>%
  rename(nRAIpart = n) %>%
  right_join(d, by = "AMIS_ID") %>%
  as.data.frame()
d$nRAIpart <- ifelse(is.na(d$nRAIpart), 0, d$nRAIpart)
table(d$nRAIpart, useNA = "always")

d <- l %>%
  filter(IAI == 1) %>%
  group_by(AMIS_ID) %>%
  count() %>%
  rename(nIAIpart = n) %>%
  right_join(d, by = "AMIS_ID") %>%
  as.data.frame()
d$nIAIpart <- ifelse(is.na(d$nIAIpart), 0, d$nIAIpart)
table(d$nIAIpart, useNA = "always")

table(d$nRAIpart, d$nIAIpart, useNA = "always")

# default NA for no AI
roletype <- rep(NA, nrow(d))
roletype[d$nRAIpart == 0 & d$nIAIpart > 0] <- 0
roletype[d$nIAIpart == 0 & d$nRAIpart > 0] <- 1
roletype[d$nIAIpart > 0 & d$nRAIpart > 0] <- 2
table(roletype, useNA = "always")

out$all$role.type <- prop.table(table(roletype))



# SAVE --------------------------------------------------------------------
 
# fn <- paste("ARTnetWorkflow/data/artnet.NetParam", gsub(" ", "", city_name), "rda", sep = ".")
# saveRDS(out, file = fn)

#####################################################

## OUTPUTS

## Mean Degree

# Overall
md.overall.main.ARTnet_3MO_script <- out$main$md.main
md.overall.casl.ARTnet_3MO_script <- out$casl$md.casl
md.overall.inst.ARTnet_3MO_script <- out$inst$md.inst

# By Age Group
md.age.main.ARTnet_3MO_script <- out$main$nf.age.grp
md.age.casl.ARTnet_3MO_script <- out$casl$nf.age.grp
md.age.inst.ARTnet_3MO_script <- out$inst$nf.age.grp

# By Race
md.race.main.ARTnet_3MO_script <- out$main$nf.race
md.race.casl.ARTnet_3MO_script <- out$casl$nf.race
md.race.inst.ARTnet_3MO_script <- out$inst$nf.race

# By Diagnosed HIV Status
md.HIV_status.main.ARTnet_3MO_script <- out$main$nf.diag.status
md.HIV_status.casl.ARTnet_3MO_script <- out$casl$nf.diag.status
md.HIV_status.inst.ARTnet_3MO_script <- out$inst$nf.diag.status

# By Cross Partnership Degree
md.casl_cross_deg.main.ARTnet_3MO_script <- out$main$nf.deg.casl
md.main_cross_deg.casl.ARTnet_3MO_script <- out$casl$nf.deg.main


## Proportion Concurrent
prop.concurrent.main.ARTnet_3MO_script <- out$main$concurrent
prop.concurrent.casl.ARTnet_3MO_script <- out$casl$concurrent


## Mixing

# By Age - Overall
mixing.age.overall.main.ARTnet_3MO_script <- out$main$nm.age.grp_diffF
mixing.age.overall.casl.ARTnet_3MO_script <- out$casl$nm.age.grp_diffF
mixing.age.overall.inst.ARTnet_3MO_script <- out$inst$nm.age.grp_diffF

# By Age - Within Age Group
mixing.age.within_group.main.ARTnet_3MO_script <- out$main$nm.age.grp
mixing.age.within_group.casl.ARTnet_3MO_script <- out$casl$nm.age.grp
mixing.age.within_group.inst.ARTnet_3MO_script <- out$inst$nm.age.grp

# By Race - Overall
mixing.race.overall.main.ARTnet_3MO_script <- out$main$nm.race_diffF
mixing.race.overall.casl.ARTnet_3MO_script <- out$casl$nm.race_diffF
mixing.race.overall.inst.ARTnet_3MO_script <- out$inst$nm.race_diffF

# By Race - Within Race Group
mixing.race.within_group.main.ARTnet_3MO_script <- out$main$nm.race
mixing.race.within_group.casl.ARTnet_3MO_script <- out$casl$nm.race
mixing.race.within_group.inst.ARTnet_3MO_script <- out$inst$nm.race


## Mean Duration
duration.main.ARTnet_3MO_script <- durs.main.all$mean.dur.adj
duration.casl.ARTnet_3MO_script <- durs.casl.all$mean.dur.adj


## One-Time Partner Rates 

# By Main+Casual Degree
OTP.rates.by.degree.ARTnet_3MO_script <- out$inst$nf.deg.tot

# By Risk Quintile
OTP.rates.by.risk.ARTnet_3MO_script <- out$inst$nf.risk.grp

```

## 3. ARTnet Workflow Script

```{r ARTnet_Workflow_Script, eval=FALSE}
#Load ARTnet
library("ARTnet")
library("tidyverse")

#1. Epistats: Specify geographic features, as well as race stratification and total age range
#under consideration
epistats <- build_epistats(geog.lvl = "city", geog.cat = "Chicago", race = TRUE, age.limits = c(16, 29),
                            age.breaks = c(18, 24))

#2. Netparams: Specify age categories if needed, or let ARTnet determine age categories by number of
#categories desired
netparams <- build_netparams(epistats = epistats, smooth.main.dur = TRUE)

#3. Netstats: Finalize network setup
netstats <- build_netstats(epistats, netparams, expect.mort = 0.0005,
                           network.size = 1000, edges.avg = TRUE)

#4. Initialize network using `netstats` object from previous step
num <- netstats$demog$num
nw <- network::network.initialize(num, directed = FALSE)

attr.names <- names(netstats$attr)
attr.values <- netstats$attr
nw <- network::set.vertex.attribute(nw, attr.names, attr.values)
nw_main <- nw_casl <- nw_inst <- nw

# 5. Main Model

#Formula:
model_main <- ~edges +
  nodematch("age.grp", diff = TRUE) +
  nodefactor("age.grp", levels = -1) +
  nodematch("race", diff = FALSE) + #race = TRUE; omit if FALSE
  nodefactor("race", levels = -1) +
  nodefactor("deg.casl", levels = -1) +
  concurrent +
  degrange(from = 3) +
  nodematch("role.class", diff = TRUE, levels = 1:2
  )

# Target Stats
netstats_main <- c(
  edges = netstats$main$edges,
  nodematch_age.grp = netstats$main$nodematch_age.grp,
  nodefactor_age.grp = netstats$main$nodefactor_age.grp[-1],
  nodematch_race = netstats$main$nodematch_race_diffF, #If race = FALSE, value will be NULL
  nodefactor_race = netstats$main$nodefactor_race[-1],
  nodefactor_deg.casl = netstats$main$nodefactor_deg.casl[-1],
  concurrent = netstats$main$concurrent,
  degrange = 0,
  nodematch_role.class = c(0, 0)
)
cbind(netstats_main)
netstats_main <- unname(netstats_main)

# Fit model
fit_main <- netest(nw_main,
                   formation = model_main,
                   target.stats = netstats_main,
                   coef.diss = netstats$main$diss.byage,
                   set.control.ergm = control.ergm(MCMLE.maxit = 500,
                                                   SAN.maxit = 3,
                                                   SAN.nsteps.times = 3),
                   verbose = FALSE)

# 6. Casual Model

# Formula
model_casl <- ~edges +
  nodematch("age.grp", diff = TRUE) +
  nodefactor("age.grp", levels = -c(1,5)) +
  nodefactor("deg.main", levels = -3) +
  concurrent +
  degrange(from = 4) +
  nodematch("role.class", diff = TRUE, levels = 1:2) +
  #If race = TRUE:
  nodematch("race", diff = FALSE) +
  nodefactor("race", levels = -1)

# Target Stats
netstats_casl <- c(
  edges = netstats$casl$edges,
  nodematch_age.grp = netstats$casl$nodematch_age.grp,
  nodefactor_age.grp = netstats$casl$nodefactor_age.grp[-c(1,5)],
  nodefactor_deg.main = netstats$casl$nodefactor_deg.main[-3],
  concurrent = netstats$casl$concurrent,
  degrange = 0,
  nodematch_role.class = c(0, 0),
  #If race = TRUE:
  nodematch_race = netstats$casl$nodematch_race_diffF,
  nodefactor_race = netstats$casl$nodefactor_race[-1]
)
cbind(netstats_casl)
netstats_casl <- unname(netstats_casl)

# Fit model
fit_casl <- netest(nw_casl,
                   formation = model_casl,
                   target.stats = netstats_casl,
                   coef.diss = netstats$casl$diss.byage,
                   set.control.ergm = control.ergm(MCMLE.maxit = 500,
                                                   SAN.maxit = 3,
                                                   SAN.nsteps.times = 3),
                   verbose = FALSE)

# 7. One-Off Model

# Formula
model_inst <- ~edges +
  nodematch("age.grp", diff = FALSE) +
  nodefactor("age.grp", levels = -1) +
  nodefactor("risk.grp", levels = -5) +
  nodefactor("deg.tot", levels = -1) +
  nodematch("role.class", diff = TRUE, levels = 1:2) +
  #If race = TRUE
  nodematch("race", diff = FALSE) +
  nodefactor("race", levels = -1)

# Target Stats
netstats_inst <- c(
  edges = netstats$inst$edges,
  nodematch_age.grp = sum(netstats$inst$nodematch_age.grp),
  nodefactor_age.grp = netstats$inst$nodefactor_age.grp[-1],
  nodefactor_risk.grp = netstats$inst$nodefactor_risk.grp[-5],
  nodefactor_deg.tot = netstats$inst$nodefactor_deg.tot[-1],
  nodematch_role.class = c(0, 0),
  #If race = TRUE
  nodematch_race = netstats$inst$nodematch_race_diffF,
  nodefactor_race = netstats$inst$nodefactor_race[-1]
)
cbind(netstats_inst)
netstats_inst <- unname(netstats_inst)

# Fit model
fit_inst <- netest(nw_inst,
                   formation = model_inst,
                   target.stats = netstats_inst,
                   coef.diss = dissolution_coefs(~offset(edges), 1),
                   set.control.ergm = control.ergm(MCMLE.maxit = 500,
                                                   SAN.maxit = 3,
                                                   SAN.nsteps.times = 3),
                   verbose = FALSE)

# 8. Save Data

# out <- list(fit_main, fit_casl, fit_inst)
# saveRDS(out, file = "netest.rda")
# 
# out2 <- list(netstats_main, netstats_casl, netstats_inst)
# saveRDS(out2, file = "netstats.rda")


#####################################################

## OUTPUTS

## Mean Degree

# Overall
md.overall.main.ARTnet_workflow_script <- netparams$main$md.main
md.overall.casl.ARTnet_workflow_script <- netparams$casl$md.casl
md.overall.inst.ARTnet_workflow_script <- netparams$inst$md.inst

# By Age Group
md.age.main.ARTnet_workflow_script <- netparams$main$nf.age.grp
md.age.casl.ARTnet_workflow_script <- netparams$casl$nf.age.grp
md.age.inst.ARTnet_workflow_script <- netparams$inst$nf.age.grp

# By Race
md.race.main.ARTnet_workflow_script <- netparams$main$nf.race
md.race.casl.ARTnet_workflow_script <- netparams$casl$nf.race
md.race.inst.ARTnet_workflow_script <- netparams$inst$nf.race

# By Diagnosed HIV Status
md.HIV_status.main.ARTnet_workflow_script <- netparams$main$nf.diag.status
md.HIV_status.casl.ARTnet_workflow_script <- netparams$casl$nf.diag.status
md.HIV_status.inst.ARTnet_workflow_script <- netparams$inst$nf.diag.status

# By Cross Partnership Degree
md.casl_cross_deg.main.ARTnet_workflow_script <- netparams$main$nf.deg.casl
md.main_cross_deg.casl.ARTnet_workflow_script <- netparams$casl$nf.deg.main


## Proportion Concurrent
prop.concurrent.main.ARTnet_workflow_script <- netparams$main$concurrent
prop.concurrent.casl.ARTnet_workflow_script <- netparams$casl$concurrent


## Mixing

# By Age - Overall
# Note: These terms are not output by netparams
# mixing.age.overall.main.ARTnet_workflow_script <- netparams$main$nm.age.grp_diffF
# mixing.age.overall.casl.ARTnet_workflow_script <- netparams$casl$nm.age.grp_diffF
# mixing.age.overall.inst.ARTnet_workflow_script <- netparams$inst$nm.age.grp_diffF

# By Age - Within Age Group
mixing.age.within_group.main.ARTnet_workflow_script <- netparams$main$nm.age.grp
mixing.age.within_group.casl.ARTnet_workflow_script <- netparams$casl$nm.age.grp
mixing.age.within_group.inst.ARTnet_workflow_script <- netparams$inst$nm.age.grp

# By Race - Overall
mixing.race.overall.main.ARTnet_workflow_script <- netparams$main$nm.race_diffF
mixing.race.overall.casl.ARTnet_workflow_script <- netparams$casl$nm.race_diffF
mixing.race.overall.inst.ARTnet_workflow_script <- netparams$inst$nm.race_diffF

# By Race - Within Race Group
mixing.race.within_group.main.ARTnet_workflow_script <- netparams$main$nm.race
mixing.race.within_group.casl.ARTnet_workflow_script <- netparams$casl$nm.race
mixing.race.within_group.inst.ARTnet_workflow_script <- netparams$inst$nm.race


## Mean Duration
duration.main.ARTnet_workflow_script <- netparams$main$durs.main.byage$mean.dur.adj
duration.casl.ARTnet_workflow_script <- netparams$casl$durs.casl.byage$mean.dur.adj


## One-Time Partner Rates

# By Main+Casual Degree
OTP.rates.by.degree.ARTnet_workflow_script <- netparams$inst$nf.deg.tot

# By Risk Quintile
OTP.rates.by.risk.ARTnet_workflow_script <- netparams$inst$nf.risk.grp

```
